\speculake: Hiding Malware in Speculative Execution

### 2018-11-29 paper/paper.tex
add triggers section
fix formatting

\documentclass[conference]{IEEEtran}

@@

\begin{document}
\title{\speculake: Hiding Malware in Speculative Execution} % TODO: replace with your title
\author{\IEEEauthorblockN{Anonymized for Review}
% \IEEEauthorblockA{Georgia Institute of Technology\\
% someemail@somedomain.com}
% \and
% \IEEEauthorblockN{Homer Simpson}
% \IEEEauthorblockA{Twentieth Century Fox\\
% homer@thesimpsons.com}
% \and
% \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
% \IEEEauthorblockA{Starfleet Academy\\
% someemail@somedomain.com}
}

\IEEEoverridecommandlockouts
\makeatletter\def\@IEEEpubidpullup{9\baselineskip}\makeatother
\IEEEpubid{\parbox{\columnwidth}{Permission to freely reproduce all or part
    of this paper for noncommercial purposes is granted provided that
    copies bear this notice and the full citation on the first
    page. Reproduction for commercial purposes is strictly prohibited
    without the prior written consent of the Internet Society, the
    first-named author (for reproduction of an entire paper only), and
    the author's employer if the paper was prepared within the scope
    of employment.
}
\hspace{\columnsep}\makebox[\columnwidth]{}}

@@

>>>>

\documentclass[conference]{IEEEtran}
\pagestyle{plain}

@@

\begin{document}
\title{\speculake: Hiding Malware in Speculative Execution} % TODO: replace with your title
\author{\IEEEauthorblockN{Jack Wampler}
\IEEEauthorblockA{University of Colorado Boulder\\
jack.wampler@colorado.edu}
\and
\IEEEauthorblockN{Ian Martiny}
\IEEEauthorblockA{University of Colorado Boulder\\
ian.martiny@colorado.edu}
\and
\IEEEauthorblockN{Eric Wustrow}
\IEEEauthorblockA{University of Colorado Boulder\\
ewust@colorado.edu}
% \IEEEauthorblockA{Georgia Institute of Technology\\
% someemail@somedomain.com}
% \and
% \IEEEauthorblockN{Homer Simpson}
% \IEEEauthorblockA{Twentieth Century Fox\\
% homer@thesimpsons.com}
% \and
% \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
% \IEEEauthorblockA{Starfleet Academy\\
% someemail@somedomain.com}
}
\IEEEoverridecommandlockouts
\makeatletter\def\@IEEEpubidpullup{6.5\baselineskip}\makeatother
\IEEEpubid{\parbox{\columnwidth}{
    Network and Distributed Systems Security (NDSS) Symposium 2019\\
    24-27 February 2019, San Diego, CA, USA\\
    ISBN 1-891562-55-X\\
    https://dx.doi.org/10.14722/ndss.2019.23409\\
    www.ndss-symposium.org
}
\hspace{\columnsep}\makebox[\columnwidth]{}}

@@

\input{triggers}
